### 2016-08-24 Chapters/PaperSummary.tex
Remove useless pictures

As a by-product of the 4-component implementation, we were able to obtain and visualize \acs{MEP} maps
from 4-component \acs{SCF} wave functions. These add yet another interpretive tool to the toolbox available
in the 4-component relativistic regime.
\todo[inline]{Recalculate MEP maps and reobtain these plots using ParaView.}
\begin{figure}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\missingfigure{Reobtain this figure: H2O\_MEP-diff-pcmdc-dc}
\caption{\ce{H2O}: $\mathrm{MEP}_\mathrm{PCM-DC} - \mathrm{MEP}_\mathrm{DC}$}
\label{fig:H2Odiff_pcmdc-dc}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\missingfigure{Reobtain this figure: H2Po\_MEP-diff-pcmdc-dc}
\caption{\ce{H2Po}: $\mathrm{MEP}_\mathrm{PCM-DC} - \mathrm{MEP}_\mathrm{DC}$}
\label{fig:H2Podiff_pcmdc-dc}
\end{subfigure}
\caption[Molecular electrostatic potential (\acs{MEP}) maps for \ce{H2O} and \ce{H2Po} at
  the \acs{DFT}/PBE0 level of theory.]{
  Molecular electrostatic potential (\acs{MEP}) maps for \ce{H2O} and \ce{H2Po} at
  the \acs{DFT}/PBE0 level of theory.
  The isocontours are in the range $[-0.02, 0.02] \si{\hartree\per\elementarycharge}$ and are
  color-coded from red to blue.
  The values plotted are differences between the values obtained for the
  Hamiltonians referred to in the subcaptions. The geometry optimized \emph{in
  vacuo}, using the \acl{DC} Hamiltonian as reference.
  \acs{PCM}-\acs{DC}: \acl{DC} in water, \acs{DC}: \acl{DC} \emph{in vacuo}.}
\label{fig:MEP_maps}
\end{figure}
The interface to \DIRAC was later released in the 2014 and later versions,
providing \acs{PCM} capabilities to the software package.

@@

\begin{figure}[tb]
 \centering
  \includegraphics[width=\textwidth]{gfx/wemlin/alpha_convergence.png}
  \caption[Convergence of $\alpha_\mathrm{iso}$ with respect to the number of molecular
  electrostatic potential (MEP) evaluation points on the cavity surface.]
  {Convergence of $\alpha_\mathrm{iso}$ with respect to the number of
   molecular electrostatic potential (MEP) evaluation points on the cavity
   surface.
   The values reported are in $a_0^3$ and refer to benzene.
   The lower axis reports the average area for the collocation
   tesselation, while the upper axis refers to the patch level in the
   wavelet Galerkin discretization. The annotation report the number of
   MEP evaluation points.
   The compression parameter triplet was set to $a = 2.5,\ d^\prime =
   2.0,\ b = 0.01$ for the piecewise constant wavelets and to $a = 2.5,\
   d^\prime = 3.0,\ b = 0.01$ for piecewise bilinear wavelets.
   The limit value is extrapolated from the results obtained from the
   piecewise bilinear wavelet Galerkin scheme.}
  \label{fig:alpha_convergence}
\end{figure}

@@

\begin{figure}[tb]
  \centering
  \begin{subfigure}[t]{.49\linewidth}
  \centering
  % Figure8a <--> dipole_acetone_perpendicular
  \includegraphics[width=\textwidth]{gfx/spherical/width.png}
  \caption{Width effect}
  \label{fig:profile_dipole_acetone_width}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{.49\linewidth}
  \centering
  % Figure8b <--> curv_fullprofile_dip_acetone
  \includegraphics[width=\textwidth]{gfx/spherical/radius.png}
  \caption{Radius effect}
  \label{fig:profile_dipole_acetone_fullprofile}
  \end{subfigure}

  \begin{subfigure}[t]{.49\linewidth}
  \centering
  % Figure8c <--> curv_dip_acetone
  \includegraphics[width=\textwidth]{gfx/spherical/curvature.png}
  \caption{Curvature effect}
  \label{fig:profile_dipole_acetone_curvature}
  \end{subfigure}
  \caption[Width, radius and curvature effect on the dipole moment of acetone for water-air droplet phase transfer.]
  {Dipole moment profiles for acetone (with dipole moment
  perpendicular to the interface) transfer at water droplet in air, for
  varying interface widths, values of $R_0$ and the curvature effect on
  dipole moment, respectively.}
  \label{fig:profile_dipole_acetone}
\end{figure}

>>>>

As a by-product of the 4-component implementation, we were able to obtain and visualize \acs{MEP} maps
from 4-component \acs{SCF} wave functions. These add yet another interpretive tool to the toolbox available
in the 4-component relativistic regime.
The interface to \DIRAC was later released in the 2014 and later versions,
providing \acs{PCM} capabilities to the software package.

@@

@@
